---
title: "p8105_hw1_yz4436"
author: "Yuanhao Zhang"
output: github_document
date: "2022-09-22"
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1
Code to load the penguins dataset from a package "palmerpenguins" containing the penguins dataset:
```{r penguinsdatasets}
data("penguins", package = "palmerpenguins")
```

In order to get the mean of flipper length, I dropped NA in flipper_length_mm column and then calculate the mean later in my description.
```{r}
penguins_withoutna = drop_na(penguins)
```


* The data in this dataset, including names / values of important variables.
  * There are eight variables in the dataset, which are named as species, island,    bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year.
* The size of the dataset (using nrow and ncol)
  * There are `r nrow(penguins)` rows and `r ncol(penguins)` columns of the dataset, which is a dataset with a size of `r nrow(penguins)` * `r ncol(penguins)`.
* The mean flipper length
  * The mean of flipper_length_mm is `r mean(pull(penguins_withoutna, flipper_length_mm))`.

Using ggplot and geom_point() to make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable. I use penguins_withoutna instead of penguins to avoid warning of NA.
```{r}
ggplot(penguins_withoutna, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 
ggsave("scatterplot for Problem 1 in HW1.pdf")
```

## Problem 2

Creating a data frame comprised of 4 different type of variables, which are norm_samp, norm_samp_positive, char_samp, factor_samp.
```{r}
sample_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_positive = norm_samp > 0,
  char_samp = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_samp = factor(c("10", "50", "10", "90", "10", "50", "50", "90", "50", "90"))
)
```

Tring to use mean() and pull() to take the mean of each variable in my dataframe.
```{r}
mean(pull(sample_df, norm_samp))
mean(pull(sample_df, norm_samp_positive))
mean(pull(sample_df, char_samp))
mean(pull(sample_df, factor_samp))
```
* What works and what doesn’t?
  * I try to take the mean of all four variables. The first variable norm_samp and the second variable norm_samp_positive works, and the third variable char_samp and the fourth variable factor_samp does not work and return NA.

Applying the as.numeric function to the logical, character, and factor variables to convert the type of variables to numeric. Usinh eval = FALSE to show the chunk but not the output.
```{r, eval = FALSE}
as.numeric(pull(sample_df, norm_samp_positive))
as.numeric(pull(sample_df, char_samp))
as.numeric(pull(sample_df, factor_samp))
```
* After applying the as.numeric function to the logical, character, and factor variables. I found that logical variable changes to 0 of False and 1 of True, character variable changes to NA since letter could not be converted to numeric, and factor variable changes to 1 of 10, 2 of 50, and 3 of 90 since I have three levels that ranked all 10 as level 1, all 50 as level 2, and all 90 as level 3. 
* When using pull function to take the mean, mean of double and logical variables could represent the real mean of themselves, so taking the mean of them works, but there is no actual meaning of the mean of characters and factors, so taking the mean of them does not work. Hence, this help explain what happened.