---
title: "p8105_hw1_yz4436"
author: "Yuanhao Zhang"
output: github_document
date: "2022-09-22"
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1
Code to load the penguins dataset from a package "palmerpenguins" containing the penguins dataset:
```{r penguinsdatasets}
data("penguins", package = "palmerpenguins")
```

In order to get the mean of flipper length, I dropped NA in flipper_length_mm column and then calculate the mean later in my description.
```{r}
penguins_withoutna = drop_na(penguins)
```


* The data in this dataset, including names / values of important variables.
  * There are eight variables in the dataset, which are named as species, island,    bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year.
* The size of the dataset (using nrow and ncol)
  * There are `r nrow(penguins)` rows and `r ncol(penguins)` columns of the dataset, which is a dataset with a size of `r nrow(penguins)` * `r ncol(penguins)`.
* The mean flipper length
  * The mean of flipper_length_mm is `r mean(pull(penguins_withoutna, flipper_length_mm))`.

Using ggplot and geom_point() to make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable. I use penguins_withoutna instead of penguins to avoid warning of NA.
```{r}
ggplot(penguins_withoutna, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 
ggsave("scatterplot for Problem 1 in HW1.pdf")
```

## Problem 2

Creating a data frame comprised of 4 different type of variables, which are norm_samp, norm_samp_positive, char_samp, factor_samp.
```{r}
sample_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_positive = norm_samp > 0,
  char_samp = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_samp = factor(c("10", "50", "10", "90", "10", "50", "50", "90", "50", "90"))
)
```

Tring to use mean() and pull() to take the mean of each variable in my dataframe.
```{r}
mean(pull(sample_df, norm_samp))
mean(pull(sample_df, norm_samp_positive))
mean(pull(sample_df, char_samp))
mean(pull(sample_df, factor_samp))
```
* What works and what doesn’t?
  * I try to take the mean of all four variables. The first variable norm_samp and the second variable norm_samp_positive works, and the third variable char_samp and the fourth variable factor_samp does not work and return NA.
