---
title: "p8105_hw1_yz4436"
author: "Yuanhao Zhang"
output: github_document
date: "2022-09-22"
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Problem 1
Code to load the penguins dataset from a package "palmerpenguins" containing the penguins dataset:
```{r penguinsdatasets}
data("penguins", package = "palmerpenguins")
```

In order to get the mean of flipper length, I dropped NA in flipper_length_mm column and then calculate the mean later in my description.
```{r}
penguins_withoutna = drop_na(penguins)
```


* The data in this dataset, including names / values of important variables.
  * There are eight variables in the dataset, which are named as species, island,    bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year.
* The size of the dataset (using nrow and ncol)
  * There are `r nrow(penguins)` rows and `r ncol(penguins)` columns of the dataset, which is a dataset with a size of `r nrow(penguins)` * `r ncol(penguins)`.
* The mean flipper length
  * The mean of flipper_length_mm is `r mean(pull(penguins_withoutna, flipper_length_mm))`.

Using ggplot and geom_point() to make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable. I use penguins_withoutna instead of penguins to avoid warning of NA.
```{r}
ggplot(penguins_withoutna, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 
ggsave("scatterplot for Problem 1 in HW1.pdf")
```
